---
output:
  html_document: default
  word_document: default
  pdf_document: default
---
# *Project*
### Arir Allana
### 17.05.2021
# *Analysis of the Retail E-commerce Market in Pakistan*
## Research Question: What are the market trends of online retail in Pakistan?

## Introduction
In the past few years, e-commerce has seen a rise in Pakistan thanks to the growing number of mobile users and greater internet access. With new and reliable local retailers such as daraz.pk, symbios.pk etc the public confidence in using e-commerce platforms has increased and so has the demand for online goods and services.
## Problem Statement
This study will summarize various fields such as best-selling category, visualize aspects like payment method and order status frequency, find correlations between multiple variables of interest and apply inferential statistical methodologies

##Importance of Research
E-commerce is of high importance to developing nations such as Pakistan which are looking to maximize their growth and make a shift towards a digital economy. Various local e-commerce startups can provide employment to a young workforce and have the potential to contribute to exports as they expand.  


## Data Description and Visulaization
The type of variables are both continuous and categorical. The variables include item_id, status, created_at, sku, price, qty_ordered, grand_total, increment_id, category_name_1, sales_commission_code, discount_amount, payment_method, Working Date, BI Status,  MV, Year, Month, Customer Since, M-Y, FY and Customer ID.

## Exploratory Data Analysis
Importing dataset
```{r}
Results <- read.csv("C:/Users/arir.allana/Desktop/CS/Stats II/Pakistan Largest Ecommerce Dataset.csv")
```
Removing NA values
#exclude blank records
```{r}
na_vec<-which(!complete.cases(Results))
complete<-Results[-na_vec,]
```

Visualizing Categories
```{r}
#table of categories
table(complete$category_name_1)
#bar chart for categories
cat <- table(complete$category_name_1)
barplot(cat, main="Categories",xlab="Category",ylab="number",las=2, cex.names=.4, cex.lab=0.7)
```

Visualizing payment method
```{r}
#table of payment method
pm <- table(complete$payment_method)
#bar chart of payment method
barplot(pm, main="payment method", xlab="method", ylab="number",las=2, cex.names=.5, cex.lab=0.7)
```

Visualizing order status

```{r}
#table of order status
st <- table(complete$status)
#bar chart of payment method
barplot(st, main="order status", xlab="status", ylab="number",las=2, cex.names=.5, cex.lab=0.7)
```

Summarizing price
```{r}
#summary of price
pr <- as.numeric(complete$price)
summary(pr)
```

Summarizing qty ordered
```{r}
#summary of qty ordered
qt <- as.numeric(complete$qty_ordered)
summary(qt)
```

Summarizing discount
```{r}
#summary of discount
ds <- as.numeric(complete$discount_amount)
summary(ds)
```

Visualizing orders freq by year
```{r}
#histogram of orders freq by year
orders_by_year <- (complete$Year)
hist(orders_by_year)

```
Summary by year
```{r}
#summary of 2016
library(dplyr)
yr_2016<-complete%>%filter(complete$Year==2016)
summary(yr_2016[, c("status", "price", "qty_ordered", "grand_total", "category_name_1", "discount_amount", "payment_method")])

#summary of 2017
yr_2017<-complete%>%filter(complete$Year==2017)
summary(yr_2017[, c("status", "price", "qty_ordered", "grand_total", "category_name_1", "discount_amount", "payment_method")])

#summary of 2018
yr_2018<-complete%>%filter(complete$Year==2018)
summary(yr_2018[, c("status", "price", "qty_ordered", "grand_total", "category_name_1", "discount_amount", "payment_method")])

```